\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage{geometry}

\pagestyle{empty}
\setlength{\tabcolsep}{0in}
\hyphenchar\font=-1
\geometry{a4paper, twoside} 
\setstretch{1}
\usepackage{booktabs}
\usepackage{topcapt}
%%%%%%%%%%%%

%%%%%%%%%%%%
% PDF setup
\usepackage{hyperref}
\hypersetup{colorlinks,breaklinks,
            linkcolor=blue,urlcolor=blue,
            anchorcolor=blue,citecolor=blue,
    	    pdftitle={Wayne Steven D. See},
	    pdfauthor={Wayne Steven D. See},
    	    pdfsubject={Resume},
    	    pdfkeywords={resume, j2ee, python, java, unix}
}

%%%%%%%%%%%%

\usepackage[dvipsnames,usenames]{color}
\usepackage{simplemargins}
\usepackage{graphicx}
\setleftmargin{1.5cm}
\setrightmargin{2cm}
\settopmargin{1.0cm}
\setbottommargin{0cm}

\newfont{\skillfont}{cmr10 at 9pt}

\newcommand{\blocktitle}[1]{
	\vspace{1mm}
	\textcolor{MidnightBlue}{
{\sc {#1}
	\vspace*{1mm}
	\hrule}
	\vspace*{1.5mm}
} }

\newenvironment{skillblock}[1]{\blocktitle{#1}\begin{tabular}{p{4cm}p{13cm}}}{\end{tabular}}
\newcommand{\skill}[2]{\noindent\raggedright{\skillfont{#1}} & #2}

\newcommand{\sectionheader}[3]{
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & \\
\emph{#2} & \emph{#3}
\end{tabular*}
}

\newenvironment{longtext}[1]{\small {#1}}

\newcommand{\heading}[4]{
\begin{center}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr}
&\huge{\textbf{\sc{#1}}}&\\
\href{mailto:#2}{\small #2} & \small #3 & \small Mobile: #4\\
\hline\hline
\end{tabular*}
\end{center}
}

\newcommand{\shortskip}[0]{\vspace{2.0mm}\\}

\setlength{\parindent}{0in}

\begin{document}
\heading{Wayne Steven D. See}{wayne.steven.see@gmail.com}{711 Camba St., Binondo, Manila, Philippines}{(+63) 917-7940763}
\blocktitle{Experience}
\sectionheader{Orange \& Bronze Software Labs, Ltd. Co.}{Senior Software Engineer and Trainer}{September 2007 to Present}
\begin{longtext}
Assisted in trainings held by the company for clients. Training topics included Java fundamentals
and best practices, Java Servlets, and Java frameworks such as Spring and Hibernate. Also tasked
in developing a proof of concept project for a client that used Adobe technologies (Adobe Flex
and Flash Media Server).
\shortskip
Currently assigned as team leader for offshore client that is developing a product targeted for use
by healthcare professionals. Technologies used include Spring, Struts, Hibernate and Swing
(client-side application deployed through Java Web Start). Development methodology used in
project is Scrum.\\
\end{longtext}
\sectionheader{RenditionDigital, Ltd.}{Java Software Engineer}{August 2007 to September 2007}
\begin{longtext}
Recruited to help in the design and implementation for product enhancements of a travel
distribution software provider. Tasks include implementing solutions that enable dynamic pricing
and distribution of multiple travel components across multiple distribution channels. Project
requires good grasp of Service-Oriented Architecture. Technologies used include SOAP web
services and EJB.\\
\end{longtext}
\sectionheader{Azeus Systems Philippines, Ltd.}{Software Developer}{June 2005 to July 2007}
\begin{longtext}
Served as developer in several of the company’s high profile projects for the Hong Kong
Government. Projects used Waterfall as software development model and followed CMMI
guidelines as an organizational process. Most of the projects involved have strict performance
guidelines and regarded as mission critical by clients. Tasks include requirements gathering and
design of functional and program specifications, as well as implementation of user interfaces and
business logic. Technologies used in projects include J2EE, HTML, JavaScript, PL/SQL and
XML, among others. Database used for projects include Oracle 8i and Oracle 10g. Application
servers used include Apache Tomcat and Oracle Application Server.
\shortskip
Also served as organization trainer for interns. Tasks include training interns on the company’s
primary technologies, including SQL, JavaScript, HTML, J2EE, PL/SQL. Also oversaw the development and implementation of two internal projects for the company. Technologies used in the internal projects include Adobe Flex 2, Adobe Integrated Runtime (AIR), Echo2 Framework,
J2EE, and SOAP web services.\\
\end{longtext}

\begin{skillblock}{Technical Proficiencies}
\skill{Languages}{Java, Ruby, Python, JavaScript, ActionScript, PL/SQL}
\shortskip
\skill{Frameworks}{Spring, iBATIS, Hibernate, Struts 2, JUnit}
\shortskip
\skill{Databases}{Oracle, PostgreSQL, MySQL}
\shortskip
\skill{Tools}{CVS, SVN, git, Hudson, Eclipse, NetBeans}
\shortskip
\skill{Operating Systems}{Windows 95/98/2000/NT/XP, Linux (Ubuntu)}
\end{skillblock}
\shortskip

\blocktitle{Education \& Certifications}
\sectionheader{Bachelor of Science in Computer Science, Major in Software Technology}{De La Salle University}{2001 to 2005}

\sectionheader{Comparative Study of Pattern Recognition Algorithms in Scoliosis Detection}{Applied Academic Activities}{2004 to 2005}
\begin{longtext}
Implemented a system that uses a variety of pattern recognition algorithms to diagnose and
detect scoliosis from digital x-ray image inputs. In charge
of system design, architecture and implementation and role in team was Project Leader. System was awarded the Silver
Medal, Most Outstanding Thesis Award.\\
\end{longtext}

\sectionheader{PhilNITS Certified}{Philippine National IT Standards Foundation (formerly known as JITSE)}{October 2006}
\shortskip
\blocktitle{Personal Background}

\begin{longtext}
Proficient in Chinese Mandarin, Chinese Fookien, English and Filipino. Interests include open source software, creative writing, chess and badminton. References can be found in \href{http://www.linkedin.com/in/waynesee}{LinkedIn}. Code samples and open source projects are available at \href{http://github.com/weynsee}{GitHub}.
\end{longtext}

\end{document}
